### 2019-04-05 thesis_proposal_LaTeX/Chapters/6_StateoftheArt.tex
progress

>>>>

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieCampSweep.png}
\decoRule
\caption[Serie C - Amplitude Sweep]{Serie C - Amplitude Sweep}
\label{fig:SerieCampSweep}
\end{figure}

The amplitude sweep results of Serie C are depicted in Figure \ref{fig:SerieCampSweep}. Similar to series A and B, results show that the storage modulus $G'$ is smaller than the loss modulus $G''$ with a parabolic behaviour. Typically, the amplitude sweep is to determine the amplitude to be used in frequency sweeps. The amplitude determined by the amplitude sweeps shall keep the material structure undisturbed is known as the linear viscoelastic region (LVER). However, no LVER was found in the samples. For that reason, the percentage of amplitude gamma $\% \gamma$ was found by trial and error. Flores discovered that a $\% \gamma = 20$ has the best performance.
